### 2020-02-04 paper/revisions/review-responses.tex

        \begin{solution}
                Thank you very much for these comments. We appreciate your detailed review, which has certainly improved the paper. The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.
        \end{solution}

        %---------------------------------------------------------------------

        \question In the SD-TMSR burnup calculation, how are the depletion regions and burnup time step defined?
        \begin{solution}

        		  Thank you for the excellent point.

        		  About depletion regions definition: we used depletion mode 1 in SERPENT-2 (i.e. burn 1), this means that the fuel material is not divided and all occurrences of it are treated as a single depletion zone. The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump.

        		  About burnup time step definition: it is time interval given in days. During burnup time step, the SD-TMSR core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%). We started our calculations by 30 days' time step but we do not find significant changes in K$_{eff}$ when we increased the time step to 365 days. The maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted 365-day as a time step for all simulation in this work.

        		  We changed the paragraph as follows:\\
        		  The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump. We used depletion mode 1 in SERPENT-2 (i.e. burn 1), this means that the fuel material is not divided and all occurrences of it are treated as a single depletion zone.

        		  We changed the paragraph as follows:\\
        		  During the depletion step, the core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%). To determine the appropriate depletion step size, we conducted a time step refinement study. We started with $\Delta t=30$days and gradually increased the depletion time step until the error in K$_{eff}$ became significant. For $\Delta t=1$year the maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted a constant, 365-day-long time step for all simulation in this work.

@@

        \end{solution}

        %---------------------------------------------------------------------
        \question During the molten salt reactor operation, part of fuel salt flows outside of reactor core then the fission reaction is not happened in external loop, however the decay reactions happens everywhere. In other words, during one burnup step, the fission reactions occur in only part of the time (depends on the ratio of time taken in fuel salt passing reactor core and external loop), and nuclides' decay or other reactions occur in the whole burnup step time. Have you considered this in SERPENT calculation?  
        \begin{solution}

		          Thank you for your insightful comment. We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input. Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region.

		          We changed the paragraph as follows:\\    
		          During the molten salt reactor operation, part of fuel salt flows outside of the reactor core then the fission reaction has not happened in the external loop, however, the decay reactions happen everywhere. We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input. Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region.     
        \end{solution}

### 2020-02-04 paper/methods.tex
Answer reviewer 1

Simulation of liquid-fueled Molten Salt Reactor (MSR) systems requires 
computational software that can support online fuel salt reprocessing and 
refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} simulates the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) full-core with various initial fuel types. This extension 
of SERPENT accounts for continuous online reprocessing and refueling 
\cite{aufiero2013extended}. The ENDF-VII.0 cross section library was used for all 
calculations in this work. The results demonstrate full-core runs of 
$1.25\times 10^7$ neutron histories per depletion step. The full burnup time of 
the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
$12$ $pcm$. The online extraction of \gls{FPs} and other neutron absorbers 
provides many benefits for MSRs. For example, it has the potential to reduce the initial 
fissile material inventory required to achieve criticality and improve the 
breeding ratio. Figure~\ref{fig:flow} shows a flow chart of the calculation 
steps.

>>>>

Simulation of liquid-fueled Molten Salt Reactor (MSR) systems requires 
computational software that can support online fuel salt reprocessing and 
refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} simulates the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) full-core with various initial fuel types. This extension 
of SERPENT accounts for continuous online reprocessing and refueling 
\cite{aufiero2013extended}. The ENDF-VII.0 cross section library was used for all 
calculations in this work. The results demonstrate full-core runs of
$1.25\times 10^7$ neutron histories per depletion step. During the depletion step, the core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%). To determine the appropriate depletion step size, we conducted a time step refinement study. We started with $\Delta t=30$days and gradually increased the depletion time step until the error in K$_{eff}$ became significant. For $\Delta t=1$year the maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted a constant, 365-day-long time step for all simulation in this work.
The full burnup time of 
the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
$12$ $pcm$. 
During the molten salt reactor operation, part of fuel salt flows outside of the reactor core then the fission reaction has not happened in the external loop, however, the decay reactions happen everywhere. We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input. Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region.

The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump. We used depletion mode 1 in Serpent-2 (i.e. burn 1), this means that the fuel material is not divided and all occurrences of it are treated as a single depletion zone.

The online extraction of \gls{FPs} and other neutron absorbers 
provides many benefits for MSRs. For example, it has the potential to reduce the initial 
fissile material inventory required to achieve criticality and improve the 
breeding ratio. Figure~\ref{fig:flow} shows a flow chart of the calculation 
steps.
